Discrete Quantum Theories and Computing

### 2018-02-28 dissertation.tex
Updates from ShareLaTeX
dissertation.tex Uploading local copy to ShareLaTeX to fix to sync problems...
dissertation.lyx "Chapter 2 Conventional Quantum Theory" Updating...

The part of conventional quantum theory (CQT) used by quantum circuit
model is described by the following:
\begin{enumerate}[label=(\roman{enumi})]
\item \label{enu:-orthonormal-basis}$D$ orthonormal basis vectors for
a Hilbert space of dimension~$D$, 
\item \label{enu:probability-amplitude}the normalized $D$ complex probability
amplitude coefficients describing the contribution of each basis vector, 
\item \label{enu:unitary-matrix}a set of probability-conserving unitary
matrix operators that suffice to describe all required state transformations, 
\item \label{enu:measurement-framework}and a measurement framework. 
\end{enumerate}
In Sec.~\ref{CQC1qubitBloch.sec}, we focus on the discrete geometric
issues raised by the properties \ref{enu:-orthonormal-basis} and
\ref{enu:probability-amplitude} given above for CQT. In Sec.~\ref{sec:Quantum-Circuit-Model},
we describe product and entangled $n$-qubit states used in quantum
circuit model, and the unitary matrices used to build circuit as addressed
by by the property \ref{enu:unitary-matrix}. In Sec.~\ref{sec:fuzzy},
we introduce the important issues of \ref{enu:measurement-framework}
and the foundations of quantum probability space.

@@

\subsection{The System Described by a Two-dimensional Hilbert Space}

@@

There is a family of 6 equivalence classes of quadratic maps that
take the remaining 3 degrees of freedom in \Eq{A5.eq} and reduce
them to 2 degrees of freedom by effectively removing $\rme^{\rmi\phi}$
(``fibering out by the circle $\Sphere{1}$''). The standard form
of this class of maps (``the Hopf fibration'') is 
\begin{eqnarray}
X & = & 2\,\mathrm{Re}\ \alpha_{0}\alpha_{1}^{*}=2x_{0}x_{1}+2y_{0}y_{1}\nonumber \\
Y & = & 2\,\mathrm{Im}\ \alpha_{0}\alpha_{1}^{*}=2x_{1}y_{0}-2x_{0}y_{1}\\
Z & = & |\alpha_{0}|^{2}-|\alpha_{1}|^{2}=x_{0}^{\ 2}+y_{0}^{\ 2}-x_{1}^{\ 2}-y_{1}^{\ 2}\ .\nonumber 
\end{eqnarray}
These transformed coordinates obey 
\begin{equation}
\|\Vec{X}\|^{2}=X^{2}+Y^{2}+Z^{2}=\left(|\alpha_{0}|^{2}+|\alpha_{1}|^{2}\right)^{2}=1\label{A7.eq}
\end{equation}
and therefore have only two remaining degrees of freedom describing
all possible distinct one-qubit quantum states. In Figure \ref{hopfFibers.fig}
we illustrate schematically the family of circles \textit{each one
of which is collapsed to a point\/} $(\theta,\phi)$ on the surface
$X^{2}+Y^{2}+Z^{2}=1$ by the Hopf map.

>>>>

The part of conventional quantum theory (CQT) used by quantum circuit
model is described by the following:
\begin{enumerate}[label=(\roman{enumi})]
\item \label{enu:-orthonormal-basis}$D$ orthonormal basis vectors for
a Hilbert space of dimension~$D$, 
\item \label{enu:probability-amplitude}the normalized $D$ complex probability
amplitude coefficients describing the contribution of each basis vector, 
\item \label{enu:unitary-matrix}a set of probability-conserving unitary
matrix operators that suffice to describe all required state transformations
of a quantum circuit, 
\item \label{enu:measurement-framework}and a measurement framework. 
\end{enumerate}
In Sec.~\ref{CQC1qubitBloch.sec}, we focus on the discrete geometric
issues raised by the properties \ref{enu:-orthonormal-basis} and
\ref{enu:probability-amplitude} given above for CQT. In Sec.~\ref{sec:Quantum-Circuit-Model},
we address the property~\ref{enu:unitary-matrix} by describing product
and entangled $n$-qubit states and unitary matrices in quantum circuit
model. In Sec.~\ref{sec:fuzzy}, we introduce the important issues
of \ref{enu:measurement-framework} and the foundations of quantum
probability space.

@@

\subsection{The single qubit problem}

@@

We can reduce 3 real degrees of freedom in \Eq{A5.eq} to 2 real
degrees of freedom by effectively removing $\rme^{\rmi\phi}$ (``fibering
out by the circle $\Sphere{1}$''). The standard form of this maps
(``the Hopf fibration'') is 
\begin{eqnarray}
X & = & 2\,\mathrm{Re}\ \alpha_{0}\alpha_{1}^{*}=2x_{0}x_{1}+2y_{0}y_{1}\,,\nonumber \\
Y & = & 2\,\mathrm{Im}\ \alpha_{0}\alpha_{1}^{*}=2x_{1}y_{0}-2x_{0}y_{1}\,,\\
Z & = & |\alpha_{0}|^{2}-|\alpha_{1}|^{2}=x_{0}^{\ 2}+y_{0}^{\ 2}-x_{1}^{\ 2}-y_{1}^{\ 2}\,.\nonumber 
\end{eqnarray}
By denoting the the three-dimensional vector~$\left(X,Y,Z\right)$
as $\Vec{X}$, \Eq{A5.eq} implies these transformed coordinates
obeying 
\begin{equation}
\|\Vec{X}\|^{2}=X^{2}+Y^{2}+Z^{2}=\left(|\alpha_{0}|^{2}+|\alpha_{1}|^{2}\right)^{2}=1\label{A7.eq}
\end{equation}
and therefore have only two remaining degrees of freedom describing
all possible distinct one-qubit quantum states. In Fig.~\ref{hopfFibers.fig},
we illustrate schematically the family of circles \textit{each one
of which is collapsed to a point\/} $(\theta,\phi)$ on the surface
$X^{2}+Y^{2}+Z^{2}=1$ by the Hopf map.
